---
title: "KPWA"
Date: November 12, 2012
output: 
html_document:
    number_sections: no
    theme: journal
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: breezedark

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)

pacman::p_load(tidyverse, psych, htmlTabbble, magrittr, reactable, xcolor, rsconnect)

ClinicalAppts <- read_csv("Data/clinicalappts11122021.csv")
Demo <- read_csv("Data/members11122021.csv")
PHQGAD <- read_csv("Data/PHQGAD11122021.csv")

Demo <- Demo %>% 
  rename(`Ginger ID` = `Employer Signups Legacy Included User ID`)

PHQGAD <- PHQGAD %>% 
  rename(`Ginger ID` = `Depression Anxiety Scores User ID`)



PHQGAD <- PHQGAD %>% 
  mutate(GAD7screen = case_when(`GAD-7 pos screen` == "Yes"~ 1,
                   `GAD-7 pos screen` == "No" ~ 0),
         PHQ9screen = case_when(`PHQ-9 pos screen` == "Yes" ~ 1,
                   `PHQ-9 pos screen` == "No" ~ 0))
  

ClinicalAppts <- ClinicalAppts %>% 
  rename(`Ginger ID` = `Clinical appts Ginger ID`)

ClinicalAppts_Count <- ClinicalAppts %>% 
  filter(`Clinical appts Appointment Status` == "Complete" | `Clinical appts Appointment Status` == "Confirmed") %>% 
  group_by(`Ginger ID`) %>% 
  count() %>% 
  rename(ClinicalSessions = n)

Master <- Demo %>% 
  full_join(ClinicalAppts_Count, by = c("Ginger ID")) %>% 
  full_join(PHQGAD, by = c("Ginger ID"))

Master$`Mapping to eligibility records (with locations, divisions etc) US State`<- as.factor(Master$`Mapping to eligibility records (with locations, divisions etc) US State`)

Master <- Master %>% 
  mutate(WA_other = case_when(`Mapping to eligibility records (with locations, divisions etc) US State` == "WA" ~ "WA",
                              TRUE ~ "Other")) %>% 
  mutate(KPWA_other = case_when(`Employer Signups Legacy Included Org` == "Kaiser Washington" ~ "KPWA",
                                TRUE ~ "Other"))

```



Questions: 

Do KPWA members have higher PHQGAD survey scores?
| No, KPWA members, on average, do not have noticeably higher PHQGAD survey scores


Do KPWA members have more clinical sessions?
| Yes, KPWA members, on average, have almost double the amount of clinical sessions

Click on column names to view by ascending/descending values

```{r echo=FALSE}
Summary <- Master %>% 
  group_by(`Mapping to eligibility records (with locations, divisions etc) US State`) %>% 
             summarise(Depression_Mean = round(mean(`Depression Anxiety Scores Depression Score`, na.rm = TRUE),2),
                       Anxiety_Mean = round(mean(`Depression Anxiety Scores Anxiety Score`, na.rm = TRUE),2),
                       ClinicalSessions_Mean = round(mean(ClinicalSessions, na.rm = TRUE),2),
                       `PHQ9_pos` = sum(PHQ9screen, na.rm = TRUE),
                       `GAD7_pos` = sum(GAD7screen, na.rm = TRUE)) 

PHQcount <- Master %>% 
    group_by(`Mapping to eligibility records (with locations, divisions etc) US State`) %>%
  count(PHQ9screen) %>% 
  subset(!is.na(PHQ9screen)) %>% 
    group_by(`Mapping to eligibility records (with locations, divisions etc) US State`) %>%
  summarise(totalPHQcount = sum(n))

GADcount <- Master %>% 
    group_by(`Mapping to eligibility records (with locations, divisions etc) US State`) %>%
  count(GAD7screen) %>% 
  subset(!is.na(GAD7screen)) %>% 
    group_by(`Mapping to eligibility records (with locations, divisions etc) US State`) %>%
  summarise(totalGADcount = sum(n))

PHQGADcount <- PHQcount %>% 
  full_join(GADcount, by = c("Mapping to eligibility records (with locations, divisions etc) US State"))

Summary <- Summary %>% 
  left_join(PHQGADcount, by = c("Mapping to eligibility records (with locations, divisions etc) US State"))

Summary <- Summary %>% 
  mutate(`PHQintake_%` = round((PHQ9_pos/totalPHQcount),2)) %>%  
  mutate(`GADintake_%` = round((GAD7_pos/totalGADcount),2))

Summary <- Summary %>% 
  arrange(desc(ClinicalSessions_Mean))

###


Summary_WA <- Master %>% 
    group_by(`WA_other`) %>% 
             summarise(Depression_Mean = round(mean(`Depression Anxiety Scores Depression Score`, na.rm = TRUE),2),
                       Anxiety_Mean = round(mean(`Depression Anxiety Scores Anxiety Score`, na.rm = TRUE),2),
                       ClinicalSessions_Mean = round(mean(ClinicalSessions, na.rm = TRUE),2))

```



```{r echo=FALSE}
Summary_org <- Master %>% 
  group_by(`Employer Signups Legacy Included Org`) %>% 
             summarise(Depression_Mean = round(mean(`Depression Anxiety Scores Depression Score`, na.rm = TRUE),2),
                       Anxiety_Mean = round(mean(`Depression Anxiety Scores Anxiety Score`, na.rm = TRUE),2),
                       ClinicalSessions_Mean = round(mean(ClinicalSessions, na.rm = TRUE),2),
                       `PHQ9_pos` = sum(PHQ9screen, na.rm = TRUE),
                       `GAD7_pos` = sum(GAD7screen, na.rm = TRUE)) 

PHQcount <- Master %>% 
    group_by(`Employer Signups Legacy Included Org`) %>%
  count(PHQ9screen) %>% 
  subset(!is.na(PHQ9screen)) %>% 
    group_by(`Employer Signups Legacy Included Org`) %>%
  summarise(totalPHQcount = sum(n))

GADcount <- Master %>% 
    group_by(`Employer Signups Legacy Included Org`) %>%
  count(GAD7screen) %>% 
  subset(!is.na(GAD7screen)) %>% 
    group_by(`Employer Signups Legacy Included Org`) %>%
  summarise(totalGADcount = sum(n))

PHQGADcount <- PHQcount %>% 
  full_join(GADcount, by = c("Employer Signups Legacy Included Org"))

Summary_org <- Summary_org %>% 
  left_join(PHQGADcount, by = c("Employer Signups Legacy Included Org"))

Summary_org <- Summary_org %>% 
  mutate(`PHQintake_%` = round((PHQ9_pos/totalPHQcount),2)) %>%  
  mutate(`GADintake_%` = round((GAD7_pos/totalGADcount),2))

Summary_org <- Summary_org %>% 
  arrange(desc(ClinicalSessions_Mean))

###


Summary_KPWA <- Master %>% 
    group_by(`KPWA_other`) %>% 
             summarise(Depression_Mean = round(mean(`Depression Anxiety Scores Depression Score`, na.rm = TRUE),2),
                       Anxiety_Mean = round(mean(`Depression Anxiety Scores Anxiety Score`, na.rm = TRUE),2),
                       ClinicalSessions_Mean = round(mean(ClinicalSessions, na.rm = TRUE),2))

Summary_org <- Summary_org %>% 
  select(-c("totalPHQcount", "totalGADcount"))

Summary <- Summary %>% 
  select(-c("totalPHQcount", "totalGADcount"))

```




# Summary {.tabset .tabset-fade}

## Across all States
```{r echo=FALSE}

Summary <- Summary %>% 
  rename(`US State` = `Mapping to eligibility records (with locations, divisions etc) US State`)


reactable(Summary)

```

## WA vs. Other States

```{r echo=FALSE}

reactable(Summary_WA)
```

## Across all orgs

```{r}
reactable(Summary_org)
```

## KPWA vs. other orgs

```{r}
reactable(Summary_KPWA)
```

```{r}
deployApp()
```

